Clean data

### 2018-07-14 01_clean-data.Rmd
Add two-level versions of gender and charity

                                     Rarely = "Never") %>% fct_rev()) %>% 

@@

                          labels = paste(c("Less than", "At least"), median(.$age))))

>>>>

                                     Rarely = "Never") %>% fct_rev(),
         give_charity_2 = fct_recode(give_charity,
                                     `At least once a year` = "Once a week",
                                     `At least once a year` = "Once a month",
                                     `At least once a year` = "Once every three months",
                                     `At least once a year` = "Once every six months",
                                     `At least once a year` = "Once a year",
                                     Rarely = "Never")) %>% 

@@

                          labels = paste(c("Less than", "At least"), median(.$age))),
         gender_bin = fct_collapse(gender,
                                   Female = "Female",
                                   `Not Female` = c("Male", "Transgender", 
                                                    "Other", "Prefer not to say")))
